```{r}
my_packages <- c("tidyverse", "data.table", "readxl",
                 "plyr",
                 "GEOquery",
                 "PharmacoGx", "Xeva",
                 "DROMA.Set")
pacman::p_load(char = my_packages)

tmp <- list()
```

# Load data
Get droma data:
```{r}
db_path <- "../../250520-DROMA_DB/sql_db/droma.sqlite"
connectDROMADatabase(db_path)

sample_anno1 <- getDROMAAnnotation("sample")
drug_anno1 <- getDROMAAnnotation("drug")

# drug_anno2 <- getDROMAAnnotation("drug")
```

```{r}
table(sample_anno1$ProjectID)
```

```{r}
PSet_gdsc2 <- readRDS("Input/PSet_GDSC2.rds")
PSet_gdsc2 <- PharmacoGx::updateObject(PSet_gdsc2)

PSet_gdsc1 <- readRDS("Input/PSet_GDSC2020.rds")
PSet_gdsc1 <- PharmacoGx::updateObject(PSet_gdsc1)

PSet_ctrp2 <- readRDS("Input/PSet_CTRPv2.rds")
PSet_ctrp2 <- PharmacoGx::updateObject(PSet_ctrp2)

PSet_prism <- readRDS("Input/PSet_PRISM.rds")
PSet_prism <- PharmacoGx::updateObject(PSet_prism)

PSet_gCSI <- readRDS("Input/PSet_gCSI2019.rds")
PSet_gCSI <- PharmacoGx::updateObject(PSet_gCSI)

PSet_ccle <- readRDS("Input/CCLE.rds")
PSet_ccle <- PharmacoGx::updateObject(PSet_ccle)

Xeva_PDXE <- readRDS("Input/Xeva_PDXE.rds")
```

# Modify the old name
```{r}
drug_anno1[drug_anno1$ProjectID %in% "GDSC1",]$ProjectID <- "archive_GDSC1"
drug_anno1[drug_anno1$ProjectID %in% "GDSC2",]$ProjectID <- "archive_GDSC2"
drug_anno1[drug_anno1$ProjectID %in% "CTRP2",]$ProjectID <- "archive_CTRP2"
drug_anno1[drug_anno1$ProjectID %in% "Prism",]$ProjectID <- "archive_Prism"


sample_anno1[sample_anno1$ProjectID %in% "GDSC1",]$ProjectID <- "archive_GDSC1"
sample_anno1[sample_anno1$ProjectID %in% "GDSC2",]$ProjectID <- "archive_GDSC2"
sample_anno1[sample_anno1$ProjectID %in% "CTRP2",]$ProjectID <- "archive_CTRP2"
sample_anno1[sample_anno1$ProjectID %in% "Prism",]$ProjectID <- "archive_Prism"

# DBI::dbWriteTable(droma_db_connection, 'sample_anno', sample_anno1, overwrite = TRUE)
# DBI::dbWriteTable(droma_db_connection, 'drug_anno', drug_anno1, overwrite = TRUE)
```

# GDSC1
## Drug
```{r}
gdsc1_sample <- PSet_gdsc1@sample
gdsc1_drug_raw <- PSet_gdsc1@treatmentResponse$profiles
gdsc1_drug_raw$label <- rownames(gdsc1_drug_raw)
gdsc_label <- str_split(gdsc1_drug_raw$label, "_")
gdsc1_drug <- separate(gdsc1_drug_raw, col = "label", into = c("cells", "drugs", "others"), sep = "_")
gdsc1_drug$AUC <- 1-gdsc1_drug$aac_recomputed
gdsc1_drug <- dcast(data.table(gdsc1_drug), cells~drugs,
                        value.var="AUC", fun.aggregate = max, fill = NA)

gdsc1_drug <- as.data.frame(gdsc1_drug)
rownames(gdsc1_drug) <- gdsc1_drug$cells
gdsc1_drug$cells <- NULL

gdsc1_drug <- as.data.frame(t(gdsc1_drug))
```

check names:
```{r}
gdsc1_drug_mapping <- checkDROMADrugNames(
  drug_names = rownames(gdsc1_drug),
  connection = droma_db_connection,
  max_distance = 0.2,              # Allow 20% character differences
  min_name_length = 5,             # Minimum length for partial matching
  keep_long_names_threshold = 18   # Keep very long names as original
)
```

```{r}
fwrite(gdsc1_drug_mapping[order(gdsc1_drug_mapping$match_confidence),], file = "Tmp/gdsc1_drug_mapping.csv")

gdsc1_drug_mapping2 <- fread("Tmp/gdsc1_drug_mapping2.csv")

gdsc1_drug_mapping2 <- gdsc1_drug_mapping2[match(rownames(gdsc1_drug), gdsc1_drug_mapping2$original_name),]
```

```{r}
rownames(gdsc1_drug) <- gdsc1_drug_mapping2$new_name

updateDROMAAnnotation(
  anno_type = "drug",
  name_mapping = gdsc1_drug_mapping2,
  project_name = "GDSC1",
  connection = droma_db_connection
)
```

check names:
```{r}
gdsc1_sample_mapping <- checkDROMASampleNames(
  sample_names = colnames(gdsc1_drug),
  connection = droma_db_connection,
  max_distance = 0.2,              # Allow 20% character differences
  min_name_length = 5             # Minimum length for partial matching
)

gdsc1_sample_mapping$new_name[gdsc1_sample_mapping$original_name %in% "NTERA-2"] <- "NTERA-S-cl-D1"
gdsc1_sample_mapping$match_confidence[gdsc1_sample_mapping$original_name %in% "NTERA-2"] <- "high"

gdsc1_sample_mapping$new_name[gdsc1_sample_mapping$original_name %in% "HARA [Human squamous cell lung carcinoma]"] <- "HARA"
gdsc1_sample_mapping$new_name[gdsc1_sample_mapping$original_name %in% "RCM-1 [Human rectum adenocarcinoma]"] <- "RCM-1"
gdsc1_sample_mapping$new_name[gdsc1_sample_mapping$original_name %in% "PL18 [Human pancreatic adenocarcinoma]"] <- "PL18"
gdsc1_sample_mapping$new_name[gdsc1_sample_mapping$original_name %in% "OMC-1 [Human cervical carcinoma]"] <- "OMC-1"

updateDROMAAnnotation(
  anno_type = "sample",
  name_mapping = gdsc1_sample_mapping,
  project_name = "GDSC1",
  connection = droma_db_connection
)

colnames(gdsc1_drug) <- gdsc1_sample_mapping$new_name
```

```{r}
# Get column names and identify duplicates
col_names <- colnames(gdsc1_drug)
unique_names <- unique(col_names)
duplicated_names <- unique_names[duplicated(col_names)]

# Function to merge duplicated columns by row means
merge_duplicates <- function(df) {
  col_names <- colnames(df)
  unique_names <- unique(col_names)
  
  # Create new dataframe with unique columns
  merged_df <- data.frame(row.names = rownames(df))
  
  for (name in unique_names) {
    # Get all columns with this name
    matching_cols <- df[, col_names == name, drop = FALSE]
    
    if (ncol(matching_cols) == 1) {
      # Single column, keep as-is
      merged_df[[name]] <- matching_cols[, 1]
    } else {
      # Multiple columns, calculate row means ignoring NA
      merged_df[[name]] <- rowMeans(matching_cols, na.rm = TRUE)
    }
  }
  
  return(merged_df)
}

# Apply the function
gdsc1_drug <- merge_duplicates(gdsc1_drug)

updateDROMADatabase(gdsc1_drug, "GDSC1_drug", overwrite = T)
```

## Dose && Con
```{r}
gdsc1_drug_dose_raw <- PSet_gdsc1@treatmentResponse[["raw"]][,,1] %>% as.data.frame()
gdsc1_drug_dose_raw$label <- rownames(gdsc1_drug_dose_raw)
gdsc1_drug_dose <- separate(gdsc1_drug_dose_raw, col = "label", into = c("cells", "drugs"), sep = "_")
gdsc1_drug_dose$cells <- setNames(gdsc1_sample_mapping$new_name, gdsc1_sample_mapping$original_name)[gdsc1_drug_dose$cells]
gdsc1_drug_dose$drugs <- setNames(gdsc1_drug_mapping2$new_name, gdsc1_drug_mapping2$original_name)[gdsc1_drug_dose$drugs]

gdsc1_drug_viability_raw <- PSet_gdsc1@treatmentResponse[["raw"]][,,2] %>% as.data.frame()
gdsc1_drug_viability_raw$label <- rownames(gdsc1_drug_viability_raw)
gdsc1_drug_viability <- separate(gdsc1_drug_viability_raw, col = "label", into = c("cells", "drugs"), sep = "_")
gdsc1_drug_viability$cells <- setNames(gdsc1_sample_mapping$new_name, gdsc1_sample_mapping$original_name)[gdsc1_drug_viability$cells]
gdsc1_drug_viability$drugs <- setNames(gdsc1_drug_mapping2$new_name, gdsc1_drug_mapping2$original_name)[gdsc1_drug_viability$drugs]
```

```{r}
updateDROMADatabase(gdsc1_drug_dose, "GDSC1_drug_dose", overwrite = T)
updateDROMADatabase(gdsc1_drug_viability, "GDSC1_drug_viability", overwrite = T)
```

# GDSC2
## Drug
```{r}
gdsc2_sample <- PSet_gdsc2@sample
gdsc2_drug_raw <- PSet_gdsc2@treatmentResponse$profiles
gdsc2_drug_raw$label <- rownames(gdsc2_drug_raw)
gdsc2_drug <- separate(gdsc2_drug_raw, col = "label", into = c("cells", "drugs", "others"), sep = "_")
gdsc2_drug$AUC <- 1-gdsc2_drug$aac_recomputed
gdsc2_drug <- dcast(data.table(gdsc2_drug), cells~drugs,
                        value.var="AUC", fun.aggregate = max, fill = NA)

gdsc2_drug <- as.data.frame(gdsc2_drug)
rownames(gdsc2_drug) <- gdsc2_drug$cells
gdsc2_drug$cells <- NULL

gdsc2_drug <- as.data.frame(t(gdsc2_drug))
```

check names:
```{r}
gdsc2_drug_mapping <- checkDROMADrugNames(
  drug_names = rownames(gdsc2_drug),
  connection = droma_db_connection,
  max_distance = 0.2,              # Allow 20% character differences
  min_name_length = 5,             # Minimum length for partial matching
  keep_long_names_threshold = 18   # Keep very long names as original
)
```

```{r}
fwrite(gdsc2_drug_mapping[order(gdsc2_drug_mapping$match_confidence),], file = "Tmp/gdsc2_drug_mapping.csv")

gdsc2_drug_mapping2 <- fread("Tmp/gdsc2_drug_mapping2.csv")

table(gdsc2_drug_mapping2$original_name %in% rownames(gdsc2_drug))
gdsc2_drug_mapping2 <- gdsc2_drug_mapping2[match(rownames(gdsc2_drug), gdsc2_drug_mapping2$original_name),]
```

```{r}
rownames(gdsc2_drug) <- gdsc2_drug_mapping2$new_name

updateDROMAAnnotation(
  anno_type = "drug",
  name_mapping = gdsc2_drug_mapping2,
  project_name = "GDSC2",
  connection = droma_db_connection
)
```

check names:
```{r}
gdsc2_sample_mapping <- checkDROMASampleNames(
  sample_names = colnames(gdsc2_drug),
  connection = droma_db_connection,
  max_distance = 0.2,              # Allow 20% character differences
  min_name_length = 5             # Minimum length for partial matching
)

gdsc2_sample_mapping$new_name[gdsc2_sample_mapping$original_name %in% "HARA [Human squamous cell lung carcinoma]"] <- "HARA"
gdsc2_sample_mapping$new_name[gdsc2_sample_mapping$original_name %in% "RCM-1 [Human rectum adenocarcinoma]"] <- "RCM-1"
gdsc2_sample_mapping$new_name[gdsc2_sample_mapping$original_name %in% "PL18 [Human pancreatic adenocarcinoma]"] <- "PL18"

updateDROMAAnnotation(
  anno_type = "sample",
  name_mapping = gdsc2_sample_mapping,
  project_name = "GDSC2",
  connection = droma_db_connection
)

colnames(gdsc2_drug) <- gdsc2_sample_mapping$new_name

table(duplicated(colnames(gdsc2_drug)))
```

```{r}
# Get column names and identify duplicates
col_names <- colnames(gdsc2_drug)
unique_names <- unique(col_names)
duplicated_names <- unique_names[duplicated(col_names)]

# Function to merge duplicated columns by row means
merge_duplicates <- function(df) {
  col_names <- colnames(df)
  unique_names <- unique(col_names)
  
  # Create new dataframe with unique columns
  merged_df <- data.frame(row.names = rownames(df))
  
  for (name in unique_names) {
    # Get all columns with this name
    matching_cols <- df[, col_names == name, drop = FALSE]
    
    if (ncol(matching_cols) == 1) {
      # Single column, keep as-is
      merged_df[[name]] <- matching_cols[, 1]
    } else {
      # Multiple columns, calculate row means ignoring NA
      merged_df[[name]] <- rowMeans(matching_cols, na.rm = TRUE)
    }
  }
  
  return(merged_df)
}

# Apply the function
gdsc2_drug <- merge_duplicates(gdsc2_drug)

updateDROMADatabase(gdsc2_drug, "GDSC2_drug", overwrite = T)
updateDROMAProjects("GDSC2")
```

## Dose && Con
```{r}
gdsc2_drug_dose_raw <- PSet_gdsc2@treatmentResponse[["raw"]][,,1] %>% as.data.frame()
gdsc2_drug_dose_raw$label <- rownames(gdsc2_drug_dose_raw)
gdsc2_drug_dose <- separate(gdsc2_drug_dose_raw, col = "label", into = c("cells", "drugs"), sep = "_")
gdsc2_drug_dose$cells <- setNames(gdsc2_sample_mapping$new_name, gdsc2_sample_mapping$original_name)[gdsc2_drug_dose$cells]
gdsc2_drug_dose$drugs <- setNames(gdsc2_drug_mapping2$new_name, gdsc2_drug_mapping2$original_name)[gdsc2_drug_dose$drugs]

gdsc2_drug_viability_raw <- PSet_gdsc2@treatmentResponse[["raw"]][,,2] %>% as.data.frame()
gdsc2_drug_viability_raw$label <- rownames(gdsc2_drug_viability_raw)
gdsc2_drug_viability <- separate(gdsc2_drug_viability_raw, col = "label", into = c("cells", "drugs"), sep = "_")
gdsc2_drug_viability$cells <- setNames(gdsc2_sample_mapping$new_name, gdsc2_sample_mapping$original_name)[gdsc2_drug_viability$cells]
gdsc2_drug_viability$drugs <- setNames(gdsc2_drug_mapping2$new_name, gdsc2_drug_mapping2$original_name)[gdsc2_drug_viability$drugs]
```

```{r}
updateDROMADatabase(gdsc2_drug_dose, "GDSC2_drug_dose", overwrite = T)
updateDROMADatabase(gdsc2_drug_viability, "GDSC2_drug_viability", overwrite = T)
```

# GDSC
## Mut
```{r}
gdsc_mutation_raw <- DBI::dbGetQuery(droma_db_connection, "SELECT * FROM GDSC_mutation_site")
gdsc_mutation_raw$feature_id <- NULL
# gdsc_mutation_raw$genes

gdsc_mutation_raw <- gdsc_mutation_raw %>%
  separate(genes, into = c("gene", "site"), sep = "_p\\.", remove = TRUE) %>%
  mutate(site = paste0("p.", site))  # Add back the "p." prefix to site
gdsc_mutation_raw$gene <- gsub("_noinfo", "", gdsc_mutation_raw$gene)
# table(gdsc_mutation_raw$site %in% "p.NA")
gdsc_mutation_raw$site[gdsc_mutation_raw$site %in% "p.NA"] <- NA
updateDROMADatabase(gdsc_mutation_raw, "GDSC_mutation_raw", overwrite = T)


gdsc_mutation_gene <- gdsc_mutation_raw %>%
  mutate(value = 1L) %>% # create the value to fill
  distinct(gene, samples, .keep_all = TRUE) %>% # if multiple, keep only one (doesn't really matter, since '1' is enough)
  pivot_wider(
    id_cols = gene, # rows
    names_from = samples, # columns
    values_from = value, # values in matrix
    values_fill = 0 # missing become 0
  ) %>% as.data.frame()
rownames(gdsc_mutation_gene) <- gdsc_mutation_gene$gene ; gdsc_mutation_gene$gene <- NULL

gdsc_mutation_raw2 <- gdsc_mutation_raw[!is.na(gdsc_mutation_raw$site),]
gdsc_mutation_raw2$gene_site <- paste0(gdsc_mutation_raw2$gene, "_", gdsc_mutation_raw2$site)

gdsc_mutation_site <- gdsc_mutation_raw2 %>%
  mutate(value = 1L) %>% # create the value to fill
  distinct(gene_site, samples, .keep_all = TRUE) %>% # if multiple, keep only one (doesn't really matter, since '1' is enough)
  pivot_wider(
    id_cols = gene_site, # rows
    names_from = samples, # columns
    values_from = value, # values in matrix
    values_fill = 0 # missing become 0
  ) %>% as.data.frame()

gdsc_mutation_site_sample_miss <- colnames(gdsc_mutation_gene)[!colnames(gdsc_mutation_gene) %in% colnames(gdsc_mutation_site)]

# Create a matrix with 0s for missing samples
missing_samples_df <- matrix(0, 
                            nrow = nrow(gdsc_mutation_site), 
                            ncol = length(gdsc_mutation_site_sample_miss))

# Set column names
colnames(missing_samples_df) <- gdsc_mutation_site_sample_miss

# Combine with existing data
gdsc_mutation_site <- cbind(gdsc_mutation_site, missing_samples_df)
rownames(gdsc_mutation_site) <- gdsc_mutation_site$gene_site ; gdsc_mutation_site$gene_site <- NULL
```

```{r}
updateDROMADatabase(gdsc_mutation_gene, "GDSC_mutation_gene", overwrite = T)
updateDROMADatabase(gdsc_mutation_site, "GDSC_mutation_site", overwrite = T)
updateDROMAProjects("GDSC")
```

# CTRP2
## Drug
```{r}
# ctrp2_sample <- PSet_ctrp2@sample
ctrp2_drug_raw <- PSet_ctrp2@treatmentResponse$profiles
ctrp2_drug_raw$label <- rownames(ctrp2_drug_raw)
ctrp2_drug <- separate(ctrp2_drug_raw, col = "label", into = c("cells", "drugs", "others"), sep = "_")
ctrp2_drug$AUC <- 1-ctrp2_drug$aac_recomputed
ctrp2_drug <- dcast(data.table(ctrp2_drug), cells~drugs,
                        value.var="AUC", fun.aggregate = max, fill = NA)

ctrp2_drug <- as.data.frame(ctrp2_drug)
rownames(ctrp2_drug) <- ctrp2_drug$cells
ctrp2_drug$cells <- NULL

ctrp2_drug <- as.data.frame(t(ctrp2_drug))
```

check names:
```{r}
ctrp2_drug_mapping <- checkDROMADrugNames(
  drug_names = rownames(ctrp2_drug),
  connection = droma_db_connection,
  max_distance = 0.2,              # Allow 20% character differences
  min_name_length = 5,             # Minimum length for partial matching
  keep_long_names_threshold = 18   # Keep very long names as original
)
```

```{r}
fwrite(ctrp2_drug_mapping[order(ctrp2_drug_mapping$match_confidence),], file = "Tmp/ctrp2_drug_mapping.csv")

ctrp2_drug_mapping2 <- fread("Tmp/ctrp2_drug_mapping2.csv")

ctrp2_drug_mapping2 <- ctrp2_drug_mapping2[match(rownames(ctrp2_drug), ctrp2_drug_mapping2$original_name),]
```

```{r}
rownames(ctrp2_drug) <- ctrp2_drug_mapping2$new_name

updateDROMAAnnotation(
  anno_type = "drug",
  name_mapping = ctrp2_drug_mapping2,
  project_name = "CTRP2",
  connection = droma_db_connection
)
```

check names:
```{r}
ctrp2_sample_mapping <- checkDROMASampleNames(
  sample_names = colnames(ctrp2_drug),
  connection = droma_db_connection,
  max_distance = 0.2,              # Allow 20% character differences
  min_name_length = 5             # Minimum length for partial matching
)

# fwrite(ctrp2_sample_mapping[order(ctrp2_sample_mapping$match_confidence),], file = "Tmp/ctrp2_sample_mapping.csv")
```

```{r}
updateDROMAAnnotation(
  anno_type = "sample",
  name_mapping = ctrp2_sample_mapping,
  project_name = "CTRP2",
  data_type = "CellLine",
  connection = droma_db_connection
)

colnames(ctrp2_drug) <- ctrp2_sample_mapping$new_name
```

```{r}
# # Get column names and identify duplicates
# col_names <- colnames(ctrp2_drug)
# unique_names <- unique(col_names)
# duplicated_names <- unique_names[duplicated(col_names)]
# 
# # Function to merge duplicated columns by row means
# merge_duplicates <- function(df) {
#   col_names <- colnames(df)
#   unique_names <- unique(col_names)
#   
#   # Create new dataframe with unique columns
#   merged_df <- data.frame(row.names = rownames(df))
#   
#   for (name in unique_names) {
#     # Get all columns with this name
#     matching_cols <- df[, col_names == name, drop = FALSE]
#     
#     if (ncol(matching_cols) == 1) {
#       # Single column, keep as-is
#       merged_df[[name]] <- matching_cols[, 1]
#     } else {
#       # Multiple columns, calculate row means ignoring NA
#       merged_df[[name]] <- rowMeans(matching_cols, na.rm = TRUE)
#     }
#   }
#   
#   return(merged_df)
# }
# 
# # Apply the function
# ctrp2_drug <- merge_duplicates(ctrp2_drug)

updateDROMADatabase(ctrp2_drug, "CTRP2_drug", overwrite = T)
```

## Dose && Con
```{r}
ctrp2_drug_dose_raw <- PSet_ctrp2@treatmentResponse[["raw"]][,,1] %>% as.data.frame()
ctrp2_drug_dose_raw$label <- rownames(ctrp2_drug_dose_raw)
ctrp2_drug_dose <- separate(ctrp2_drug_dose_raw, col = "label", into = c("cells", "drugs"), sep = "_")
ctrp2_drug_dose$cells <- setNames(ctrp2_sample_mapping$new_name, ctrp2_sample_mapping$original_name)[ctrp2_drug_dose$cells]
ctrp2_drug_dose$drugs <- setNames(ctrp2_drug_mapping2$new_name, ctrp2_drug_mapping2$original_name)[ctrp2_drug_dose$drugs]

ctrp2_drug_viability_raw <- PSet_ctrp2@treatmentResponse[["raw"]][,,2] %>% as.data.frame()
ctrp2_drug_viability_raw$label <- rownames(ctrp2_drug_viability_raw)
ctrp2_drug_viability <- separate(ctrp2_drug_viability_raw, col = "label", into = c("cells", "drugs"), sep = "_")
ctrp2_drug_viability$cells <- setNames(ctrp2_sample_mapping$new_name, ctrp2_sample_mapping$original_name)[ctrp2_drug_viability$cells]
ctrp2_drug_viability$drugs <- setNames(ctrp2_drug_mapping2$new_name, ctrp2_drug_mapping2$original_name)[ctrp2_drug_viability$drugs]
```

```{r}
updateDROMADatabase(ctrp2_drug_dose, "CTRP2_drug_dose", overwrite = T)
updateDROMADatabase(ctrp2_drug_viability, "CTRP2_drug_viability", overwrite = T)

updateDROMAProjects("CTRP2")
```

# PRISM
```{r}
# prism_drug_raw <- fread("Input/secondary-screen-dose-response-curve-parameters.csv")
```

## Drug
```{r}
# ctrp2_sample <- PSet_ctrp2@sample
prism_drug_raw <- PSet_prism@treatmentResponse$profiles
prism_drug_raw$label <- rownames(prism_drug_raw)
prism_drug <- separate(prism_drug_raw, col = "label", into = c("a1", "a2", "cell_id", "drugs"), sep = "::")
prism_sample_anno <- PSet_prism@sample
prism_drug <- merge(prism_drug,prism_sample_anno[,c(1,5)], by.x = "cell_id", by.y = "depmap_id")
prism_drug$cells <- gsub("_.*$", "", prism_drug$PRISM.sampleid)

prism_drug$AUC <- 1-prism_drug$aac_recomputed
prism_drug <- dcast(data.table(prism_drug), cells~drugs,
                        value.var="AUC", fun.aggregate = max, fill = NA)

prism_drug <- as.data.frame(prism_drug)
rownames(prism_drug) <- prism_drug$cells
prism_drug$cells <- NULL

prism_drug <- as.data.frame(t(prism_drug))
```

check names:
```{r}
prism_drug_mapping <- checkDROMADrugNames(
  drug_names = rownames(prism_drug),
  connection = droma_db_connection,
  max_distance = 0.2,              # Allow 20% character differences
  min_name_length = 5,             # Minimum length for partial matching
  keep_long_names_threshold = 18   # Keep very long names as original
)
```

```{r}
prism_drug_mapping2 <- prism_drug_mapping
prism_drug_mapping2$new_name[prism_drug_mapping2$match_type %in% "keep_original_long"] <- prism_drug_mapping2$cleaned_name[prism_drug_mapping2$match_type %in% "keep_original_long"]
prism_drug_mapping2$match_confidence[prism_drug_mapping2$match_type %in% "keep_original_long"] <- "high"

fwrite(prism_drug_mapping2[order(prism_drug_mapping2$match_confidence),], file = "Tmp/prism_drug_mapping.csv")

prism_drug_mapping3 <- fread("Tmp/prism_drug_mapping.csv")

prism_drug_mapping3 <- prism_drug_mapping3[match(rownames(prism_drug), prism_drug_mapping3$original_name),]

prism_drug_mapping4 <- prism_drug_mapping3[!prism_drug_mapping3$new_name %in% drug_anno1$DrugName,]
prism_drug_mapping3 <- prism_drug_mapping3[prism_drug_mapping3$new_name %in% drug_anno1$DrugName,]

prism_drug_mapping4$new_name <- c(
  "7-Hydroxystaurosporine", "l-Buthionine sulfoximine",
  "Carboxyamidotriazole", "Dianhydrogalactitol",
  "Estradiol Cypionate", "Flumethasone Pivalate",
  "melengestrol acetate (usan)", "mycophenolate mofetil (usan)", "phenylmercuric acetate (usan)"
)
prism_drug_mapping5 <- rbind(prism_drug_mapping3,
                             prism_drug_mapping4)
prism_drug_mapping5 <- prism_drug_mapping5[match(rownames(prism_drug), prism_drug_mapping5$original_name),]
```

```{r}
table(duplicated(prism_drug_mapping5$new_name))
table(duplicated(prism_sample_mapping$new_name))
```

```{r}
prism_drug$drugs <- prism_drug_mapping5$new_name

prism_drug_merged <- prism_drug %>%
  group_by(drugs) %>%
  dplyr::summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)), .groups = "drop") %>%
  column_to_rownames("drugs")
prism_drug <- as.data.frame(prism_drug_merged)

prism_drug[is.nan(as.matrix(prism_drug))] <- NA
```

```{r}
# rownames(prism_drug) <- prism_drug_mapping5$new_name
prism_drug_mapping6 <- prism_drug_mapping5[match(rownames(prism_drug), prism_drug_mapping5$new_name),]

updateDROMAAnnotation(
  anno_type = "drug",
  name_mapping = prism_drug_mapping6,
  project_name = "Prism",
  connection = droma_db_connection
)
```

check names:
```{r}
prism_sample_mapping <- checkDROMASampleNames(
  sample_names = colnames(prism_drug),
  connection = droma_db_connection,
  max_distance = 0.2,              # Allow 20% character differences
  min_name_length = 5             # Minimum length for partial matching
)

# fwrite(ctrp2_sample_mapping[order(ctrp2_sample_mapping$match_confidence),], file = "Tmp/ctrp2_sample_mapping.csv")
```

```{r}
colnames(prism_drug) <- prism_sample_mapping$new_name

updateDROMAAnnotation(
  anno_type = "sample",
  name_mapping = prism_sample_mapping,
  project_name = "Prism",
  data_type = "CellLine",
  connection = droma_db_connection
)
```

```{r}
updateDROMADatabase(prism_drug, "Prism_drug", overwrite = T)
```

## Dose && Con
```{r}
prism_drug_dose_raw <- PSet_prism@treatmentResponse[["raw"]][,,1] %>% as.data.frame()
prism_drug_dose_raw$label <- rownames(prism_drug_dose_raw)
prism_drug_dose <- separate(prism_drug_dose_raw, col = "label", into = c("a1", "a2", "cell_id", "drugs"), sep = "::")

prism_drug_dose <- merge(prism_drug_dose,prism_sample_anno[,c(1,5)], by.x = "cell_id", by.y = "depmap_id")
prism_drug_dose$cells <- gsub("_.*$", "", prism_drug_dose$PRISM.sampleid)
prism_drug_dose2 <- prism_drug_dose[prism_drug_dose$drugs %in% prism_drug_mapping6$original_name,]

prism_drug_dose2$cells <- setNames(prism_sample_mapping$new_name, prism_sample_mapping$original_name)[prism_drug_dose2$cells]
prism_drug_dose2$drugs <- setNames(prism_drug_mapping6$new_name, prism_drug_mapping6$original_name)[prism_drug_dose2$drugs]

# viability
prism_drug_viability_raw <- PSet_prism@treatmentResponse[["raw"]][,,2] %>% as.data.frame()
prism_drug_viability_raw$label <- rownames(prism_drug_viability_raw)
prism_drug_viability <- separate(prism_drug_viability_raw, col = "label", into = c("a1", "a2", "cell_id", "drugs"), sep = "::")

prism_drug_viability <- merge(prism_drug_viability,prism_sample_anno[,c(1,5)], by.x = "cell_id", by.y = "depmap_id")
prism_drug_viability$cells <- gsub("_.*$", "", prism_drug_viability$PRISM.sampleid)
prism_drug_viability2 <- prism_drug_viability[prism_drug_viability$drugs %in% prism_drug_mapping6$original_name,]

prism_drug_viability2$cells <- setNames(prism_sample_mapping$new_name, prism_sample_mapping$original_name)[prism_drug_viability2$cells]
prism_drug_viability2$drugs <- setNames(prism_drug_mapping6$new_name, prism_drug_mapping6$original_name)[prism_drug_viability2$drugs]
```

```{r}
prism_drug_viability <- prism_drug_viability2
prism_drug_viability <- prism_drug_viability[,-c(1,42,43,45)]
prism_drug_viability <- prism_drug_viability[,c(1:40,42,41)]

prism_drug_dose <- prism_drug_dose2
prism_drug_dose <- prism_drug_dose[,-c(1,42,43,45)]
prism_drug_dose <- prism_drug_dose[,c(1:40,42,41)]
```


```{r}
updateDROMADatabase(prism_drug_dose, "Prism_drug_dose", overwrite = T)
updateDROMADatabase(prism_drug_viability, "Prism_drug_viability", overwrite = T)

updateDROMAProjects("Prism")
```

# Xeva
## Mut
```{r}
Xeva_mutation_raw <- DBI::dbGetQuery(droma_db_connection, "SELECT * FROM Xeva_mutation_gene")
Xeva_mutation_raw$feature_id <- NULL

Xeva_mutation_gene <- Xeva_mutation_raw %>%
  mutate(value = 1L) %>% # create the value to fill
  distinct(genes, samples, .keep_all = TRUE) %>% # if multiple, keep only one (doesn't really matter, since '1' is enough)
  pivot_wider(
    id_cols = genes, # rows
    names_from = samples, # columns
    values_from = value, # values in matrix
    values_fill = 0 # missing become 0
  ) %>% as.data.frame()
rownames(Xeva_mutation_gene) <- Xeva_mutation_gene$genes ; Xeva_mutation_gene$genes <- NULL
```

```{r}
updateDROMADatabase(Xeva_mutation_gene, "Xeva_mutation_gene", overwrite = T)
updateDROMADatabase(Xeva_mutation_raw, "Xeva_mutation_raw", overwrite = T)
updateDROMAProjects("Xeva")
```

## Drug
```{r}
Xeva_drug <- DBI::dbGetQuery(droma_db_connection, "SELECT * FROM Xeva_drug")
```

# gCSI
## Mut
```{r}
gCSI_mutation_raw <- DBI::dbGetQuery(droma_db_connection, "SELECT * FROM gCSI_mutation_gene")
gCSI_mutation_raw$feature_id <- NULL
# gCSI_mutation_raw$genes

gCSI_mutation_gene <- gCSI_mutation_raw %>%
  mutate(value = 1L) %>% # create the value to fill
  distinct(genes, samples, .keep_all = TRUE) %>% # if multiple, keep only one (doesn't really matter, since '1' is enough)
  pivot_wider(
    id_cols = genes, # rows
    names_from = samples, # columns
    values_from = value, # values in matrix
    values_fill = 0 # missing become 0
  ) %>% as.data.frame()
rownames(gCSI_mutation_gene) <- gCSI_mutation_gene$genes ; gCSI_mutation_gene$genes <- NULL
```

```{r}
updateDROMADatabase(gCSI_mutation_raw, "gCSI_mutation_raw", overwrite = T)
updateDROMADatabase(gCSI_mutation_gene, "gCSI_mutation_gene", overwrite = T)
```

## Dose && Con
```{r}
gCSI_drug_dose_raw <- PSet_gCSI@treatmentResponse[["raw"]][,,1] %>% as.data.frame()
gCSI_drug_dose_raw$label <- rownames(gCSI_drug_dose_raw)
gCSI_drug_dose <- separate(gCSI_drug_dose_raw, col = "label", into = c("cells", "drugs"), sep = "_")

gCSI_drug_name_df <- data.frame(
  Name = drug_anno1[drug_anno1$ProjectRawName %in% gCSI_drug_dose$drugs &
               drug_anno1$ProjectID %in% "gCSI",]$DrugName,
  ProjectRawName = drug_anno1[drug_anno1$ProjectRawName %in% gCSI_drug_dose$drugs &
               drug_anno1$ProjectID %in% "gCSI",]$ProjectRawName
)
gCSI_sample_name_df <- data.frame(
  Name = sample_anno1[sample_anno1$ProjectRawName %in% gCSI_drug_dose$cells &
               sample_anno1$ProjectID %in% "gCSI",]$SampleID,
  ProjectRawName = sample_anno1[sample_anno1$ProjectRawName %in% gCSI_drug_dose$cells &
               sample_anno1$ProjectID %in% "gCSI",]$ProjectRawName
)


gCSI_drug_dose$cells <- setNames(gCSI_sample_name_df$Name, gCSI_sample_name_df$ProjectRawName)[gCSI_drug_dose$cells]
gCSI_drug_dose$drugs <- setNames(gCSI_drug_name_df$Name, gCSI_drug_name_df$ProjectRawName)[gCSI_drug_dose$drugs]

gCSI_drug_viability_raw <- PSet_gCSI@treatmentResponse[["raw"]][,,2] %>% as.data.frame()
gCSI_drug_viability_raw$label <- rownames(gCSI_drug_viability_raw)
gCSI_drug_viability <- separate(gCSI_drug_viability_raw, col = "label", into = c("cells", "drugs"), sep = "_")

gCSI_drug_viability$cells <- setNames(gCSI_sample_name_df$Name, gCSI_sample_name_df$ProjectRawName)[gCSI_drug_viability$cells]
gCSI_drug_viability$drugs <- setNames(gCSI_drug_name_df$Name, gCSI_drug_name_df$ProjectRawName)[gCSI_drug_viability$drugs]
```

```{r}
updateDROMADatabase(gCSI_drug_dose, "gCSI_drug_dose", overwrite = T)
updateDROMADatabase(gCSI_drug_viability, "gCSI_drug_viability", overwrite = T)

updateDROMAProjects("gCSI")
```

# CCLE
## Mut
```{r}
ccle_mutation_raw <- DBI::dbGetQuery(droma_db_connection, "SELECT * FROM CCLE_mutation_site")
# ccle_mutation_raw$genes

ccle_mutation_raw <- ccle_mutation_raw %>%
  separate(genes, into = c("gene", "site"), sep = "_p\\.", remove = TRUE) %>%
  mutate(site = paste0("p.", site))  # Add back the "p." prefix to site
ccle_mutation_raw$gene <- gsub("_noinfo", "", ccle_mutation_raw$gene)
# table(gdsc_mutation_raw$site %in% "p.NA")
ccle_mutation_raw$site[ccle_mutation_raw$site %in% "p.NA"] <- NA
updateDROMADatabase(ccle_mutation_raw, "CCLE_mutation_raw", overwrite = T)

ccle_mutation_gene <- unique(ccle_mutation_raw[,c(1,3)]) %>%
  mutate(value = 1L) %>% # create the value to fill
  distinct(gene, samples, .keep_all = TRUE) %>% # if multiple, keep only one (doesn't really matter, since '1' is enough)
  pivot_wider(
    id_cols = gene, # rows
    names_from = samples, # columns
    values_from = value, # values in matrix
    values_fill = 0 # missing become 0
  ) %>% as.data.frame()
rownames(ccle_mutation_gene) <- ccle_mutation_gene$gene ; ccle_mutation_gene$gene <- NULL
updateDROMADatabase(ccle_mutation_gene, "CCLE_mutation_gene", overwrite = T)

updateDROMADatabase(ccle_mutation_raw, "CCLE_mutation_raw", overwrite = T)

ccle_mutation_raw2 <- ccle_mutation_raw[!is.na(ccle_mutation_raw$site),]
ccle_mutation_raw2$gene_site <- paste0(ccle_mutation_raw2$gene, "_", ccle_mutation_raw2$site)

ccle_mutation_site <- unique(ccle_mutation_raw2[,c(3:4)])
# ccle_mutation_site <- unique(ccle_mutation_raw2[,3:4]) %>%
#   mutate(value = 1L) %>% # create the value to fill
#   distinct(gene_site, samples, .keep_all = TRUE) %>% # if multiple, keep only one (doesn't really matter, since '1' is enough)
#   pivot_wider(
#     id_cols = gene_site, # rows
#     names_from = samples, # columns
#     values_from = value, # values in matrix
#     values_fill = 0 # missing become 0
#   ) 
# 
# # Combine with existing data
# rownames(ccle_mutation_site) <- ccle_mutation_site$gene_site; ccle_mutation_site$gene_site <- NULL
```

save as sparse mtx:
```{r}
# ccle_mutation_site2 <- as(as.matrix(ccle_mutation_site), "dgCMatrix")
```

save as long df firstly:
```{r}
updateDROMADatabase(ccle_mutation_site, "CCLE_mutation_site", overwrite = T)
```

## Fusion
```{r}
ccle_fusion_raw <- DBI::dbGetQuery(droma_db_connection, "SELECT * FROM CCLE_fusion")

ccle_fusion <- ccle_fusion_raw %>%
  mutate(value = 1L) %>% # create the value to fill
  distinct(genes, samples, .keep_all = TRUE) %>% # if multiple, keep only one (doesn't really matter, since '1' is enough)
  pivot_wider(
    id_cols = genes, # rows
    names_from = samples, # columns
    values_from = value, # values in matrix
    values_fill = 0 # missing become 0
  ) %>% as.data.frame()
rownames(ccle_fusion) <- ccle_fusion$genes ; ccle_fusion$genes <- NULL
```

```{r}
updateDROMADatabase(ccle_fusion, "CCLE_fusion", overwrite = T)
updateDROMADatabase(ccle_fusion_raw, "CCLE_fusion_raw", overwrite = T)
```

## Dose && Con
```{r}
ccle_drug_dose_raw <- PSet_ccle@treatmentResponse[["raw"]][,,1] %>% as.data.frame()
ccle_drug_dose_raw$label <- rownames(ccle_drug_dose_raw)
# ccle_drug_dose <- separate(ccle_drug_dose_raw, col = "label", into = c("others", "drugs", "cells"), sep = "_")
# 
# table(ccle_drug_dose$drugs %in% drug_anno1$ProjectRawName)
# table(ccle_drug_dose$cells %in% sample_anno1$ProjectRawName)
# 
# table(ccle_drug_dose$drugs %in% drug_anno1$DrugName)
# table(ccle_drug_dose$cells %in% sample_anno1$SampleID)
```

```{r}
# a1 <- unique(ccle_drug_dose$drugs[!ccle_drug_dose$drugs %in% drug_anno1$ProjectRawName])
# a2 <- unique(ccle_drug_dose$cells[!ccle_drug_dose$cells %in% sample_anno1$ProjectRawName])
```

```{r}
CCLE_anno_drug <- PSet_ccle@treatmentResponse[["info"]]
CCLE_anno_drug$label <- rownames(CCLE_anno_drug)
ccle_drug_dose <- merge(
  ccle_drug_dose_raw,
  CCLE_anno_drug[,c(1,2,16)],
  by = "label"
)

ccle_drug_viability_raw <- PSet_ccle@treatmentResponse[["raw"]][,,2] %>% as.data.frame()
ccle_drug_viability_raw$label <- rownames(ccle_drug_viability_raw)
ccle_drug_viability <- merge(
  ccle_drug_viability_raw,
  CCLE_anno_drug[,c(1,2,16)],
  by = "label"
)

table(ccle_drug_dose$treatmentid %in% drug_anno1$ProjectRawName)
table(ccle_drug_viability$sampleid %in% sample_anno1$ProjectRawName)
```

check sample names:
```{r}
ccle_sample_mapping <- checkDROMASampleNames(
  sample_names = unique(ccle_drug_viability$sampleid),
  connection = droma_db_connection,
  max_distance = 0.2,              # Allow 20% character differences
  min_name_length = 5             # Minimum length for partial matching
)

ccle_sample_mapping$new_name[ccle_sample_mapping$original_name %in% "HARA [Human squamous cell lung carcinoma]"] <- "HARA"

table(ccle_drug_viability$sampleid %in% ccle_sample_mapping$original_name)
```


```{r}
ccle_drug_name_df <- data.frame(
  Name = drug_anno1[drug_anno1$ProjectRawName %in% ccle_drug_dose$treatmentid &
               drug_anno1$ProjectID %in% "CCLE",]$DrugName,
  ProjectRawName = drug_anno1[drug_anno1$ProjectRawName %in% ccle_drug_dose$treatmentid &
               drug_anno1$ProjectID %in% "CCLE",]$ProjectRawName
)

ccle_drug_dose$cells <- setNames(ccle_sample_mapping$new_name, ccle_sample_mapping$original_name)[ccle_drug_dose$sampleid]
ccle_drug_dose$drugs <- setNames(ccle_drug_name_df$Name, ccle_drug_name_df$ProjectRawName)[ccle_drug_dose$treatmentid]

ccle_drug_viability$cells <- setNames(ccle_sample_mapping$new_name, ccle_sample_mapping$original_name)[ccle_drug_viability$sampleid]
ccle_drug_viability$drugs <- setNames(ccle_drug_name_df$Name, ccle_drug_name_df$ProjectRawName)[ccle_drug_viability$treatmentid]
```

```{r}
ccle_drug_viability$label <- NULL; ccle_drug_viability$treatmentid <- NULL; ccle_drug_viability$sampleid <- NULL
ccle_drug_dose$label <- NULL; ccle_drug_dose$treatmentid <- NULL; ccle_drug_dose$sampleid <- NULL
```


```{r}
updateDROMADatabase(ccle_drug_viability, "CCLE_drug_viability", overwrite = T)
updateDROMADatabase(ccle_drug_dose, "CCLE_drug_dose", overwrite = T)

updateDROMAProjects("CCLE")
```

# Modify all drug to AAC and scale to 0-1
```{r}
all_drug_data <- getFeatureFromDatabase(  
  select_feas_type = "drug",  
  select_feas = "all",  # or specify particular drugs  
  data_sources = "all"  
)
```

```{r}
UMPDO1_drug_raw <- all_drug_data[["UMPDO1"]]
UMPDO2_drug_raw <- all_drug_data[["UMPDO2"]]
UMPDO3_drug_raw <- all_drug_data[["UMPDO3"]]
CTRP1_drug_raw <- all_drug_data[["CTRP1"]]
Xeva_drug_raw <- all_drug_data[["Xeva"]]
LICOB_drug_raw <- all_drug_data[["LICOB"]]
# HKUPDO_drug_raw <- all_drug_data[["HKUPDO"]]

updateDROMADatabase(UMPDO1_drug_raw, "UMPDO1_drug_raw", overwrite = T)
updateDROMADatabase(UMPDO2_drug_raw, "UMPDO2_drug_raw", overwrite = T)
updateDROMADatabase(UMPDO3_drug_raw, "UMPDO3_drug_raw", overwrite = T)
updateDROMADatabase(CTRP1_drug_raw, "CTRP1_drug_raw", overwrite = T)
updateDROMADatabase(Xeva_drug_raw, "Xeva_drug_raw", overwrite = T)
updateDROMADatabase(LICOB_drug_raw, "LICOB_drug_raw", overwrite = T)
```

Ref: https://www.perplexity.ai/search/i-have-ic50-emax-and-auc-not-i-6Zy6iB6ETzCHwJ7cvvdCqA#0
dividing each AUC by the maximum dose used for that compound (exactly what the DepMap team recommends

```{r}
UMPDO1_drug <- UMPDO1_drug_raw/60
UMPDO2_drug <- UMPDO2_drug_raw/20

UMPDO3_drug <- UMPDO3_drug_raw
UMPDO3_drug[UMPDO3_drug>20] <- 20
UMPDO3_drug <- UMPDO3_drug/20
CTRP1_drug <- apply(CTRP1_drug_raw, MARGIN = 2, FUN = function(x){
  x/max(na.omit(x))
})
Xeva_drug <- apply(Xeva_drug_raw, MARGIN = 2, FUN = function(x){
  x/max(na.omit(x))
})
LICOB_drug <- apply(LICOB_drug_raw, MARGIN = 2, FUN = function(x){
  x/max(na.omit(x))
})

all_drug_data$CTRP1 <- CTRP1_drug
all_drug_data$UMPDO1 <- UMPDO1_drug
all_drug_data$UMPDO2 <- UMPDO2_drug
all_drug_data$UMPDO3 <- UMPDO3_drug
all_drug_data$Xeva <- Xeva_drug
all_drug_data$LICOB <- LICOB_drug
```

```{r}
# Batch process all drug data
process_all_drug_data <- function(all_drug_data) {
  # Get the names of all datasets
  dataset_names <- names(all_drug_data)
  
  cat("Processing", length(dataset_names), "datasets...\n")
  
  for (i in seq_along(dataset_names)) {
    dataset_name <- dataset_names[i]
    
    cat("Processing dataset", i, "of", length(dataset_names), ":", dataset_name, "\n")
    
    # Get the current dataset
    current_data <- all_drug_data[[dataset_name]]
    
    # Convert AUC to AAC (1 - AUC)
    aac_data <- 1 - current_data
    
    # Save to database
    tryCatch({
      updateDROMADatabase(aac_data, paste0(dataset_name, "_drug"), overwrite = T)
    }, error = function(e) {
      cat("Error processing", dataset_name, ":", e$message, "\n")
    })
  }
  
  cat("Batch processing completed!\n")
}
```

```{r}
# Execute the batch processing
process_all_drug_data(all_drug_data)
```

# Clean the archive anno

# Save
